The SMT Competition 2015--2018

### 2019-04-12 2018/report/SMT-COMP.tex
Report: TODO 22
Report: TODO 19: Minor things

The 2018 release of the SMT Library contained 336,844 non-incremental
benchmarks in 51 logics, as well as~10,167 incremental benchmarks
(with a total of nearly 32 million {\tt check-sat} commands) in 26
logics.  Table~\ref{table:smtlib} presents further data on the size of
the SMT Library since~2015.  While the library usually grows from one
year to the next because of the inclusion of new benchmarks and
logics, continuous curation efforts may also cause benchmarks to be
removed or reclassified on occasion, thereby causing individual logics
or even the entire library to shrink.  From~2015 to~2018, the total
number of benchmarks has increased by~68\,\%.  The largest benchmark
in the 2018 release had a size of 1,041~MB; the total size of the
release was 91~GB.

@@

Each track is further split into (logic) \emph{divisions}, where each
division corresponds to a logic from the SMT Library.
Table~\ref{table:divisions} shows the number of divisions in each
track since~2015.  Participants can choose which tracks and divisions
they want to enter, and competition results are reported separately
for each track and division.  Thus, competing solvers need not support
all logics, and may or may not support features such as incrementality
or unsat-core generation.

@@

Another paradigm shift concerns the treatment of benchmarks with
unknown status.  Because of the difficulty to judge solver responses
for such benchmarks, SMT Competitions until 2015 only used benchmarks
whose status was known (i.e., that had been solved previously by
existing SMT solvers).  In 2015, 30,717 non-incremental benchmarks
from the SMT Library were not used for the competition because their
status was unknown.  However, this approach was criticized for
favoring imitation of existing solvers over true innovation.  In~2016,
the SMT Library contained 29,724 non-incremental benchmarks with
unknown status; solver performance on these was evaluated but reported
separately.  Since 2017, all non-incremental benchmarks are eligible
for the competition's Main track regardless of status, and they
directly affect the competition results.  Solver responses for such
benchmarks are assumed to be correct, unless there is a disagreement
between two or more (otherwise sound) solvers.  Benchmarks with
disagreements are removed from the competition results.  In 2016,
there were disagreements on 79 benchmarks; in 2017, only one benchmark
was removed; and in 2018, there were no disagreements between
otherwise sound solvers.

@@

StarExec typically reserves between~80 to~150 machines for the SMT
Competition, allowing its workload to be completed within two to three
weeks.  By these measures, the SMT Competition has become not only one
of the heaviest users of StarExec, but also one of the largest
competitions in automated reasoning.

@@

In 2014, the SMT Competition was part of the FLoC Olympic Games.
These gave the competition increased visibility and sponsored three
Kurt G\"odel medals.  After substantial internal debate, the 2014
competition organizers decided to award these to the winner of the
Main track's QF\_BV division (which had historically been the logic
with the largest number of solver submissions and job pairs), as well
as to the two best Main-track solvers according to a competition-wide
ranking that had been instituted especially for this
purpose~\cite{CDW14}.  This ranking emphasizes breadth of solver
participation---a solver participating in many logics need not be the
best in any one of them to rank highly.

The competition-wide ranking for the Main track was retained and
refined after~2014.  Table~\ref{table:competition-wide-ranking} shows
the best three solvers according to this ranking for 2015--2018.  Also
shown is Z3, which ranked highly each year but was running hors
concours.  Sequential and parallel performance are reported
separately.
%
Note that scores are not directly comparable between different years:
the set of benchmarks changes from one year to the next, and also the
formula to compute the score changed (see below).  Moreover, readers
should keep in mind that this ranking---like any method that maps the
performance of solvers for a broad range of logics to a
one-dimensional value---is inherently limited.  We refer to the
individual division rankings (Section~\ref{sec:division-rankings}) for
more detailed information about each solver.

@@

The 2018 edition of the competition was again part of the FLoC Olympic
Games, which sponsored seven medals.  The competition organizers
awarded these to the following solvers:
\begin{itemize}
\item The best three Main-track solvers according to the
  competition-wide ranking (CVC4, Yices2, and SMTInterpol; see
  Table~\ref{table:competition-wide-ranking}),
\item the solvers that won the QF\_BV division in the Main track
  (Boolector and MinkeyRink; see Table~\ref{tab:winners-main}),
\item the solver that won the most competitive divisions in the
  Application track (Yices2),
\item the solver that won the most competitive divisions in the
  Unsat-Core track (Yices2).
\end{itemize}

>>>>

The 2018 release of the SMT Library contained 336,844 non-incremental
benchmarks in 51 logics, as well as~10,167 incremental benchmarks
(with a total of nearly 32 million {\tt check-sat} commands) in 26
logics.  Table~\ref{table:smtlib} presents further data on the size of
the SMT Library since~2015.  While the library usually grows from one
year to the other because of the inclusion of new benchmarks and
logics, continuous curation efforts may also cause benchmarks to be
removed or reclassified on occasion, thereby causing individual logics
or even the entire library to shrink.  From~2015 to~2018, the total
number of benchmarks has increased by~68\,\%.  The largest benchmark
in the 2018 release had a size of 1,041~MB; the total size of the
release was 91~GB.

@@

Each track is further split into (logic) \emph{divisions}, where each
division corresponds to a logic from the SMT Library.
Table~\ref{table:divisions} shows the number of divisions in each
track since~2015.  Participants can choose which tracks and divisions
they want to enter, and competition results are reported separately
for each track and division.  Thus, competing solvers do not need support
all logics, and may or may not support features such as incrementality
or unsat-core generation.

@@

Another paradigm shift concerns the treatment of benchmarks with
unknown status.  Because of the difficulty to judge solver responses
for such benchmarks, SMT Competitions until 2015 only used benchmarks
whose status was known (i.e., that had been solved previously by
existing SMT solvers).  In 2015, 30,717 non-incremental benchmarks
from the SMT Library were not used for the competition because their
status was unknown.  However, this approach was criticized for
imitating existing solvers rather than truly innovating.  In~2016,
the SMT Library contained 29,724 non-incremental benchmarks with
unknown status; solver performance on these was evaluated but reported
separately.  Since 2017, all non-incremental benchmarks are eligible
for the competition's Main track regardless of status, and they
directly affect the competition results.  Solver responses for such
benchmarks are assumed to be correct, unless there is a disagreement
between two or more (otherwise sound) solvers.  Benchmarks with
disagreements are removed from the competition results.  In 2016,
there were disagreements on 79 benchmarks; in 2017, only one benchmark
was removed; and in 2018, there were no disagreements between
otherwise sound solvers.

@@

StarExec typically reserves between~80 to~150 machines for the SMT
Competition, allowing its workload to be completed within two to three
weeks.

@@

In 2014, the SMT Competition was part of the FLoC Olympic Games.
These gave the competition increased visibility and sponsored three
Kurt G\"odel medals.  After substantial internal debate, the 2014
competition organizers decided to award these to the winner of the
Main track's QF\_BV division (which had historically been the logic
with the largest number of solver submissions and job pairs), as well
as to the two best Main-track solvers according to a competition-wide
ranking that had been instituted especially for this
purpose~\cite{CDW14}.  This ranking emphasizes breadth of solver
participation---a solver participating in many logics does not need to be the
best in any one of them to rank highly.

The competition-wide ranking for the Main track was retained and
refined after~2014.  Table~\ref{table:competition-wide-ranking} shows
the best three solvers according to this ranking for 2015--2018.  Also
shown is Z3, which ranked highly each year but was running hors
concours.  Sequential and parallel performance are reported
separately.
%
Note that scores are not directly comparable between different years:
the set of benchmarks changes from one year to the other, and also the
formula to compute the score changed (see below).  Moreover, readers
should keep in mind that this ranking---like any method that maps the
performance of solvers for a broad range of logics to a
one-dimensional value---is inherently limited.  We refer to the
individual division rankings (Section~\ref{sec:division-rankings}) for
more detailed information about each solver.

@@

The 2018 edition of the competition was again part of the FLoC Olympic
Games, which sponsored seven medals.  The competition organizers
awarded the following solvers:
\begin{itemize}
\item The best three Main-track solvers according to the
  competition-wide ranking (CVC4, Yices2, and SMTInterpol; see
  Table~\ref{table:competition-wide-ranking}),
\item the solvers that won the QF\_BV division in the Main track
  (Boolector and MinkeyRink; see Table~\ref{tab:winners-main}),
\item the solver that won the most competitive divisions in the
  Application track (Yices2),
\item the solver that won the most competitive divisions in the
  Unsat-Core track (Yices2).
\end{itemize}
